---
title: "p8105_hw5_jys2136"
author: "Jocelyn Sun"
date: "11/17/2021"
output: github_document
---

```{r, setup, message = FALSE, echo = TRUE, results = 'hide'}

library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_bw()) + theme(axis.text.x = element_text(size = 9),
                              axis.text.y = element_text(size = 9),
                              legend.position = "bottom")

```

# Problem 1

```{r, homicide_df}

homicide_df = 
  read_csv("homicide-data.csv",  na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")

```

Focusing on Baltimore, MD
```{r, baltimore_df}

baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")


baltimore_summary =
  baltimore_df %>% 
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
    )


baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n))


baltimore_test %>% 
  broom::tidy() %>% 
  knitr::kable()

```


```{r, prop_test_function}

prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
      summarise(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  
  return(city_test)
  
}

# trying for another city 
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function() %>% 
  broom::tidy() %>% 
  knitr::kable()

```


```{r, iteration}

results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
    ) %>% 
    select(city_state, tidy_results) %>% 
    unnest(tidy_results) %>% 
    select(city_state, estimate, starts_with("conf"))

head(results_df) %>% 
  knitr::kable()

```


```{r}

results_df %>% 
  filter(city_state != "TulsaAL") %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +  
  theme(axis.text.x = element_text(size = 7, angle = 90, vjust = 0.5, hjust = 1))
  
``` 

# Problem 2

```{r, tidying_data}

longstudy_df = 
  tibble(path = list.files("./data", full.names = TRUE)) %>% 
  mutate(data = purrr::map(.x = path, ~read_csv(.x))) %>% 
  unnest(data) %>%
  separate(path, c("dot", "folder", "txt"), sep = "/") %>%
  separate(txt, c("txt_arm","sub_id", "file")) %>%
  select(-c("dot", "folder", "file")) %>%
  pivot_longer(
    week_1:week_8, 
    names_to = "week", 
    names_prefix = "week_",
    values_to = "values"
  ) %>%
  mutate(
    week = as.factor(week)
  )

knitr::kable(longstudy_df, caption  = "**Table 1: Finalized Longitudinal Study Dataframe**")

```

Spaghetti plot

```{r, spaghetti_plot}

longstudy_df %>% 
  mutate(txt_arm = recode(txt_arm, 
                          "con" = "control",
                          "exp" = "experiment")) %>%
  ggplot(aes(x = week, y = values, group = sub_id, color = sub_id)) + 
  geom_line() + 
  labs(
    title = "Fig 1: Subject Observations Over Time by Treatment Arm",
    x = "Time (weeks)",
    y = "Observed Values"
  ) + 
  scale_color_hue(name = "Participant ID") +
  facet_grid(. ~ txt_arm)

```

#### Data Observations
In general, for all participants, the observed values of the experiment arm over time are higher than the control arm. Although observed values of some participants in the experiment arm at week 1 may have started out lower than the observed values in the control arm, all observed values in the experiment arm are greater than the observed values of the control arm at week 8. 

# Problem 3

```{r, iris_loading_data}

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()

```


```{r, iris_replacement}

iris_clean = function(x){
    
  if (is.numeric(x)) {
    x = replace_na(x, mean(x, na.rm = TRUE))
  } 
  else if (is.character(x)) {
       x = replace_na(x, "virginica")
  }
  
}

iris_df = map(iris_with_missing, iris_clean) %>% 
  as_tibble() 

knitr::kable(iris_df, caption  = "**Table 2: Finalized Iris Dataframe**")

```




